Hospitalizations for psychiatric conditions among adolescents during the COVID-19 pandemic

### 2021-08-28 psy_peds.Rmd
fixing hospitalization length count

## Adding columns with hospitalization number and hospitalization length to the clinical raw file
```{r}
count_sequences_hospitalisation <- function(df, ...) {
  count_sequences <- rle(df$in_hospital)
  count_sequences_1 <- lapply(count_sequences, function(x) x[count_sequences$values == 1])
  n_sequences <- seq_along(count_sequences_1$lengths)
  sequences <- rep.int(n_sequences, count_sequences_1$lengths)
  sequences_len <- rep.int(count_sequences_1$lengths, count_sequences_1$lengths)
  df[df$in_hospital == 1, "n_hospitalisation"] <- sequences
  df[df$in_hospital == 1, "len_hospitalisation"] <- sequences_len
  return(df)
}
clinical_raw <- clinical_raw %>%
  group_by(patient_num) %>% 
  group_modify(count_sequences_hospitalisation)
```

@@

### Data management for the patientClinicalCourse table
```{r}
clinical_raw <- clinical_raw %>% 
  dplyr::mutate( date = as.Date( calendar_date, format = dateFormat ),
                 weeks = as.Date(cut( date, breaks = "week")),
                 month = as.Date(cut( date, breaks = "month")),
                 year = format( date, "%Y"), 
                 period = ifelse( date < pandemic_start_date,
                                  "before_pandemic","during_pandemic")) %>% 
  dplyr::filter(cohort  %in% c("AllAdm", "AllNotAdm"))
```

>>>>

## Adding columns with hospitalization number and hospitalization length to the clinical raw file
```{r}
count_sequences_hospitalisation <- function(df, ...) {
  # TODO: To be optimized to make it faster 
  total_span <- data.frame(total_span = seq(min(df$days_since_admission),
                    max(df$days_since_admission))
  )
  total_span <- left_join(total_span, df[,c("in_hospital", "days_since_admission")],
            by = c("total_span" = "days_since_admission")
  ) %>% replace_na(list(in_hospital = 0))
  count_sequences <- rle(total_span$in_hospital)
  count_sequences_1 <- lapply(count_sequences, function(x) x[count_sequences$values == 1])
  n_sequences <- seq_along(count_sequences_1$lengths)
  sequences <- rep.int(n_sequences, count_sequences_1$lengths)
  sequences_len <- rep.int(count_sequences_1$lengths, count_sequences_1$lengths)
  df[df$in_hospital == 1, "n_hospitalisation"] <- sequences
  df[df$in_hospital == 1, "len_hospitalisation"] <- sequences_len
  return(df)
}
clinical_raw <- clinical_raw %>%
  group_by(patient_num, cohort) %>% 
  group_modify(count_sequences_hospitalisation)
```

@@

### Data management for the patientClinicalCourse table
```{r}
clinical_raw <- clinical_raw %>% 
  dplyr::mutate( date = as.Date( calendar_date, format = dateFormat ),
                 weeks = as.Date(cut( date, breaks = "week")),
                 month = as.Date(cut( date, breaks = "month")),
                 year = format( date, "%Y"), 
                 period = ifelse( date < pandemic_start_date,
                                  "before_pandemic","during_pandemic")) %>% 
  dplyr::filter(cohort  %in% c("AllAdm"))
```
